\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-01-01 article.tex
Added intro and special cases to Classification

  In this section we describe where the data originates, and then elaborate on
  the approach taken to register and investigate the dataset.

@@

  Suitable tags were attached to every movement by first extracting keywords
  from their English description, and second adding more detailed tags while
  performing the pattern.

  The first movement in Chon-Ji, for instance, is to ``[m]ove the left foot to
  B, forming a left walking stance toward B while executing a low block to B
  with the left forearm\cite{cyclo:vol1}.'' Removing the verbose parts of the
  description we are left with:

@@

% TODO: introduction

@@

        right\_technique\}$.

>>>>

  In this section we describe where the data originates. Next we elaborate on
  the approach taken to register and investigate the dataset. Finally, we have
  a look at how each movement has been classified with emphasis on special
  cases.

@@

  Suitable tags were attached to every movement by first extracting keywords
  from their English description, and then adding more detailed tags while
  performing the pattern.

  The first movement in Chon-Ji, for instance, is to ``[m]ove the left foot to
  B, forming a left walking stance toward B while executing a low block to B
  with the left forearm\cite{cyclo:vol1}.'' Removing the verbose parts of the
  description leaves us with:

@@

  Classification is done by attaching metadata, in terms of tags, to each
  pattern movement. In most cases, applying tags to movements have been
  straightforward. However, there are movements that need special mention.
  These movements fall into two categories.

  The first category consist of movements where both arms are part of the
  technique by either forming the technique, or by being two separate
  techniques in a single movement.

  When both arms are used in one technique, the movement has been tagged with
  $\{left\_technique, \: right\_technique\}$ to reflect that both arms are
  needed for the technique, or that the movement contains two separate hand
  techniques.

  An example of a movement where both arms are required to form the technique
  can be found in the 13\textsuperscript{th} movement of Joong-Gun Tul, which
  is \emph{Gunnun so kyocha joomuk chukyo makgi}.

  When it comes to a movement with two separate hand techniques, the
  27\textsuperscript{th} movement of Joong-Gun Tul, being \emph{Nachuo so
  sonbadak noollo makgi}, serves as a nice illustration.

  The implications of tagging movements with $\{left\_technique, \:
  right\_technique\}$ is that the total amount of hand techniques on either
  side are higher than what actually is the case. This flaw does not affect
  the bias we are investigating.

  The second category comprises ambiguous movements, and thus contain
  clarification on why certain tags were added.

  Below is a list of all the special cases from both categories.

@@

        right\_technique\}$. This increases the total amount of punches on
